---
title: "London-lockdown feature selection - Overall"
author: "Andrew Mitchell"
date: "11/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load data

```{r load data, results='hide', message=FALSE, warning=FALSE}
# library(tidyverse)
library(here)
library(dplyr)
library(readxl)
library(MASS)
library(caret)
# library(car)
library(olsrr) 
library(glue) 

# ssid.data <- read_excel(here("Data", "2020-04-21", "AllLondon_combined_200421.xlsx"))
ssid.data <- read.csv(here("data", "2020-08-11", "LondonBINResults_2020-08-10.csv"))
# ssid.data$Natural = ordered(ssid.data$Natural, levels=c("1", "2", "3", "4", "5"))
# ssid.data$overall = ordered(ssid.data$overall, levels=c("1", "2", "3", "4", "5"))

# Set GroupID, SessionID, Location as factor type
ssid.data <- ssid.data %>% mutate_at(vars(GroupID, SessionID, LocationID,
                                          Lockdown),
                                     funs(as.factor))
ssid.data <- ssid.data %>% mutate_at(vars(Natural, overall, Pleasant,
                                          Eventful),
                                     funs(as.numeric))
##################################################################
```

For our starting acoustic variables, I need to cut it down to start. First, I'm removing all of the psychoacoustic_min variables.
I'll also remove the THD_freq features. The SII is not designed for environmental sound, so we'll remove it. The LCeq_LAeq and LA10_LA90 have been producing terrible collinearity issues, so we'll remove them up front.

```{r}
acoustic_vars = c("FS", "FS_5", "FS_10", "FS_50", "FS_90", "FS_95", "FS_Min", "FS_Max", "FS_5.FS_95", "FS_10.FS_90", "FS_Max.FS_Min", "LAeq", "LAeq_5", "LAeq_10", "LAeq_50", "LAeq_90", "LAeq_95", "LAeq_Max", "LAeq_Min", "LAeq_10.LAeq_90", "LAeq_5.LAeq_95", "LAeq_Max.LAeq_Min", "N_5", "N_10", "N_50", "N_90", "N_95", "N_Min", "N_Max", "N_5.N_95", "N_10.N_90", "N_Max.N_Min", "R", "R_5", "R_10", "R_50", "R_90", "R_95", "R_Min", "R_Max", "R_5.R_95", "R_10.R_90", "R_Max.R_Min", "S", "S_5", "S_10", "S_50", "S_90", "S_95", "S_Min", "S_Max", "S_5.S_95", "S_10.S_90", "S_Max.S_Min", "SIL_5", "SIL_10", "SIL_50", "SIL_90", "SIL_95", "SIL_Min", "SIL_Max", "SIL_5.SIL_95", "SIL_10.SIL_90", "SIL_Max.SIL_Min", "T_5", "T_10", "T_50", "T_90", "T_95", "T_Max", "T_5.T_95", "T_10.T_90", "SpectralCentroid", "MaxFreq", "PeakSpectralCentroid", "PeakMaxFreq")

# "FS_M0", "FS_nrmse0", "LAeq_M0", "LAeq_nrmse0", "N_M0", "N_nrmse0", "N_M1", "N_nrmse1", "N_M2", "N_nrmse2", "R_M0", "R_nrmse0", "S_M0", "S_nrmse0", "S_M1", "S_nrmse1", "S_M2", "S_nrmse2", "SIL_M0", "SIL_nrmse0", "T_M0", "T_nrmse0"

dep_vars = c("Natural", "overall", "Pleasant", "Eventful")

# # Standardise
# ssid.data <- ssid.data %>%
#     mutate_at(acoustic_vars, ~(scale(.) %>% as.vector))
 
# Cutdown the dataset
ssid.data <- ssid.data[c("GroupID", "LocationID", "Lockdown", dep_vars, acoustic_vars)]

london.compress <- ssid.data %>% 
    group_by(GroupID) %>%
    summarize_at(.vars = c(dep_vars, acoustic_vars), mean)

london.compress['LocationID'] <- unique(ssid.data[c('GroupID', 'LocationID')])['LocationID']
london.compress['Lockdown'] <- unique(ssid.data[c('GroupID', 'Lockdown')])['Lockdown']

# Standardise
london.compress <- london.compress %>%
    mutate_at(acoustic_vars, ~(scale(.) %>% as.vector))

head(london.compress)

# Split the dataset according to its lockdown status
dataframes <- split(london.compress, london.compress$Lockdown)
prelockdown.data <- dataframes[[1]]
lockdown.data <- dataframes[[2]]

# # cut down the data set
prelockdown.data <- data.frame(na.omit(prelockdown.data))


```

## Feature selection for 'overall' model

First we need to apply a filter for the repeated features - i.e. determine which of each type of psychoacoustic feature to include. For example, for Loudness, we have the 7 statistical features and 3 variation features. We know we won't be including all, or even more than one, of each of these, so we should start by cutting out the redundant ones.

To do this we need to calculate some sort of simple prediction accuracy metric for each individual feature to the output variable. If output is categorical, I recommend AUC.

### Filtering features
```{r}
max_corr <- function(feature_list, target_variable, data) {
    cor_table <- cor(data[feature_list], data[target_variable])
    max_feature <- rownames(cor_table)[which.max(abs(cor_table))]
    max_value <- cor_table[which.max(abs(cor_table))]
    results <- c(max_feature, max_value)
    results
}

FS_stats <- c("FS", "FS_5", "FS_10", "FS_50", "FS_90", "FS_95", "FS_Min", "FS_Max")
FS_variation <- c("FS_5.FS_95", "FS_10.FS_90", "FS_Max.FS_Min")
LAeq_stats <- c("LAeq", "LAeq_5", "LAeq_10", "LAeq_50", "LAeq_90", "LAeq_95", "LAeq_Max", "LAeq_Min")
LAeq_variation <- c("LAeq_10.LAeq_90", "LAeq_5.LAeq_95", "LAeq_Max.LAeq_Min")
N_stats <- c("N_5", "N_10", "N_50", "N_90", "N_95", "N_Min", "N_Max")
N_variation <- c("N_5.N_95", "N_10.N_90", "N_Max.N_Min")
R_stats <- c("R", "R_5", "R_10", "R_50", "R_90", "R_95", "R_Min", "R_Max")
R_variation <- c("R_5.R_95", "R_10.R_90", "R_Max.R_Min")
S_stats <- c("S", "S_5", "S_10", "S_50", "S_90", "S_95", "S_Min", "S_Max")
S_variation <- c("S_5.S_95", "S_10.S_90", "S_Max.S_Min")
SIL_stats <- c("SIL_5", "SIL_10", "SIL_50", "SIL_90", "SIL_95", "SIL_Min", "SIL_Max")
SIL_variation <- c("SIL_5.SIL_95", "SIL_10.SIL_90", "SIL_Max.SIL_Min")
T_stats <- c("T_5", "T_10", "T_50", "T_90", "T_95", "T_Max")
T_variation <- c("T_5.T_95", "T_10.T_90")
frequency_features <- c("SpectralCentroid", "MaxFreq", "PeakSpectralCentroid", "PeakMaxFreq")

all_features <- list(FS_stats, FS_variation, LAeq_stats, LAeq_variation, N_stats, N_variation, R_stats, R_variation, S_stats, S_variation, SIL_stats, SIL_variation, T_stats, T_variation, frequency_features) 

for(item in all_features) {
    results <- max_corr(item, "overall", prelockdown.data)
    print(results)
}


```

So our new, filtered feature set will be:

```{r}
library(lmerTest)
library(MuMIn)

overall.features <- c("FS_90", "FS_Max.FS_Min", "LAeq_10", "LAeq_10.LAeq_90", "N_5", "N_10.N_90", "R_95", "R_10.R_90", "S_Max", "S_10.S_90", "SIL_5", "SIL_10.SIL_90", "T_50", "T_10.T_90", "SpectralCentroid", "MaxFreq", "PeakSpectralCentroid", "PeakMaxFreq")

mlm.overall <- lmer(overall ~ FS_90 + FS_Max.FS_Min + LAeq_10 + LAeq_10.LAeq_90 + N_5 + N_10.N_90 + R_95 + R_10.R_90 + S_Max + S_10.S_90 + SIL_5 + SIL_10.SIL_90 + T_50 + T_10.T_90 + SpectralCentroid + MaxFreq + PeakSpectralCentroid + PeakMaxFreq + (1|LocationID), data = prelockdown.data)


# mlm.overall <- lmer(overall ~ FS_90 + FS_Max.FS_Min + LAeq_10 + LAeq_10.LAeq_90 + N_5 + N_10.N_90 + R_95 + R_10.R_90 + S_Max + S_10.S_90 + SIL_5 + SIL_10.SIL_90 + T_50 + T_10.T_90 + SpectralCentroid + MaxFreq + PeakSpectralCentroid + PeakMaxFreq + FS_M0 + FS_nrmse0 + LAeq_M0 + LAeq_nrmse0 + N_M0 + N_nrmse0 + N_M1 + N_nrmse1 + N_M2 + N_nrmse2 + R_M0 + R_nrmse0 + S_M0 + S_nrmse0 + S_M1 + S_nrmse1 + S_M2 + S_nrmse2 + SIL_M0 + SIL_nrmse0 + T_M0 + T_nrmse0 + (1|LocationID), data = london.compress)

stepMod <- lmerTest::step(mlm.overall)
stepMod
selected.mod <- get_model(stepMod)
summary(selected.mod)
r.squaredGLMM(selected.mod)
```

```{r}
library(car)
vif(selected.mod, data = prelockdown.data)
```


## Checking prediction behaviour

```{r}
prelockdown.data$overall.pred <- predict(selected.mod, newdata = prelockdown.data)
ggplot(prelockdown.data, aes(x=overall, y=overall.pred)) + geom_point() +
    geom_smooth(method=lm)
cor(prelockdown.data$overall, prelockdown.data$overall.pred)
var(prelockdown.data$overall, prelockdown.data$overall.pred)

```

```{r}
ggplot(prelockdown.data, aes(x = overall, color=LocationID)) + 
    geom_density(bw=.5)

ggplot(prelockdown.data, aes(x = overall.pred, color=LocationID)) + 
    geom_density(bw=.5)
```

```{r}
lockdown.data$overall.pred <- predict(selected.mod, newdata = lockdown.data)
ggplot(lockdown.data, aes(x = overall.pred, color=LocationID)) + 
    geom_density(bw=.5)
```

# Model for `Natural`


### Filtering features
```{r}
all_features <- list(FS_stats, FS_variation, LAeq_stats, LAeq_variation, N_stats, N_variation, R_stats, R_variation, S_stats, S_variation, SIL_stats, SIL_variation, T_stats, T_variation, frequency_features) 

for(item in all_features) {
    results <- max_corr(item, "Natural", prelockdown.data)
    print(results)
}


```

So our new, filtered feature set will be:

```{r}
overall.features <- c("FS_95", "FS_Max.FS_Min", "LAeq_5", "LAeq_5.LAeq_95", "N_Max", "N_5.N_95", "R_95", "R_5.R_95", "S_Min", "S_Max.S_Min", "SIL_Max", "SIL_5.SIL_95", "T_50", "T_10.T_90", "SpectralCentroid")

mlm.Natural <- lmer(Natural ~ FS_95 + FS_Max.FS_Min + LAeq_5 + LAeq_5.LAeq_95 + N_Max + N_5.N_95 + R_95 + R_5.R_95 + S_Min + S_Max.S_Min + SIL_Max + SIL_5.SIL_95 + T_50 + T_10.T_90 + SpectralCentroid + MaxFreq + PeakSpectralCentroid + PeakMaxFreq + (1|LocationID), data = prelockdown.data)


# mlm.overall <- lmer(overall ~ FS_90 + FS_Max.FS_Min + LAeq_10 + LAeq_10.LAeq_90 + N_5 + N_10.N_90 + R_95 + R_10.R_90 + S_Max + S_10.S_90 + SIL_5 + SIL_10.SIL_90 + T_50 + T_10.T_90 + SpectralCentroid + MaxFreq + PeakSpectralCentroid + PeakMaxFreq + FS_M0 + FS_nrmse0 + LAeq_M0 + LAeq_nrmse0 + N_M0 + N_nrmse0 + N_M1 + N_nrmse1 + N_M2 + N_nrmse2 + R_M0 + R_nrmse0 + S_M0 + S_nrmse0 + S_M1 + S_nrmse1 + S_M2 + S_nrmse2 + SIL_M0 + SIL_nrmse0 + T_M0 + T_nrmse0 + (1|LocationID), data = london.compress)

stepMod <- lmerTest::step(mlm.Natural)
stepMod
selected.mod <- get_model(stepMod)
summary(selected.mod)
r.squaredGLMM(selected.mod)

```

```{r}
library(car)
vif(selected.mod, data = prelockdown.data)
```


## Checking prediction behaviour

```{r}
prelockdown.data$Natural.pred <- predict(selected.mod, newdata = prelockdown.data)
ggplot(prelockdown.data, aes(x=Natural, y=Natural.pred)) + geom_point() +
    geom_smooth(method=lm)
cor(prelockdown.data$Natural, prelockdown.data$Natural.pred)
var(prelockdown.data$Natural, prelockdown.data$Natural.pred)

```

```{r}
ggplot(prelockdown.data, aes(x = Natural, color=LocationID)) + 
    geom_density(bw=.5)

ggplot(prelockdown.data, aes(x = Natural.pred, color=LocationID)) + 
    geom_density(bw=.5)
```

```{r}
lockdown.data$Natural.pred <- predict(selected.mod, newdata = lockdown.data)
ggplot(lockdown.data, aes(x = Natural.pred, color=LocationID)) + 
    geom_density(bw=.5)
```


```{r}

ggplot(prelockdown.data, aes(x=LocationID, y=overall)) +
    geom_boxplot()
ggplot(prelockdown.data, aes(x=LocationID, y=overall.pred)) +
    geom_boxplot()

ggplot(lockdown.data, aes(x=LocationID, y=overall.pred)) +
    geom_boxplot()
```