---
title: "Lockdown MLM building"
author: "Andrew Mitchell"
date: "14/06/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results='hide', message=FALSE, warning=FALSE}
library(here)   # file path handline
library(MASS)   # Modelling
library(readxl)
library(dplyr)  # piping
library(glue)
library(lmerTest)
library(nlme)
library(MuMIn)
library(car)

ssid.data <- read_excel(here("data", "2020-06-14", "2020-04-28_Pre-Lockdown-London_combined.xlsx"))

# Set GroupID, SessionID, Location as factor type
ssid.data <- ssid.data %>% mutate_at(vars(GroupID, SessionID, LocationID,
                                          Lockdown),
                                     funs(as.factor))
ssid.data <- ssid.data %>% mutate_at(vars(Natural, overall, Pleasant,
                                          Eventful),
                                     funs(as.numeric))
```

For our starting acoustic variables, I need to cut it down to start. First, I'm removing all of the psychoacoustic_min variables.
I'll also remove the THD_freq features. The SII is not designed for environmental sound, so we'll remove it. The LCeq_LAeq and LA10_LA90 have been producing terrible collinearity issues, so we'll remove them up front.

```{r}
acoustic_vars = c('LZeq', 'LCeq', 'LAeq', 'LAmax', 'LA_5', 'LA_10', 'LA_50', 'LA_90', 'N', 'Nmax', 'N5', 'N10', 'N50', 'N90', 'N95', 'R', 'Rmax', 'R5', 'R10', 'R50', 'R90', 'R95', 'S', 'S.1', 'Smax', 'S5', 'S10', 'S50', 'S90', 'S95', 'T', 'Tmax', 'T5', 'T10', 'T50', 'T90', 'T95', 'FS', 'FSmax', 'FS5', 'FS10', 'FS50', 'FS90', 'FS95', 'THD', 'THDmax', 'THD5', 'THD10', 'THD50', 'THD90', 'THD95', 'I', 'Imax', 'I5', 'I10', 'I50', 'I90', 'I95', 'SIL.rms.', 'SIL.av.', 'SILmin', 'SILmax', 'SIL5', 'SIL10', 'SIL50', 'SIL90', 'SIL95', 'LA5_LA95', 'SpectralCentroid', 'PeakSpectralCentroid', 'HighFreqAvg', 'PeakHighFreqAvg', 'FS_slope', 'THD_slope', 'I_slope', 'LA_slope', 'LZ_slope', 'N_slope', 'R_slope', 'S_slope', 'T_slope')

dep_vars = c("Traffic", "Other", "Natural", "Human", "overall", "Pleasant", "Eventful")

# # Standardise
ssid.data <- ssid.data %>%
    mutate_at(acoustic_vars, ~(scale(.) %>% as.vector))


# Cutdown the dataset
ssid.data <- ssid.data[c("GroupID", "LocationID", dep_vars, acoustic_vars)]

london.compress <- ssid.data %>% 
    group_by(GroupID) %>%
    summarize_at(.vars = c(dep_vars, acoustic_vars), mean)

london.compress['LocationID'] <- unique(ssid.data[c('GroupID', 'LocationID')])['LocationID']
london.compress <- data.frame(na.omit(london.compress))

# Global Mean Centering
for(variable in acoustic_vars){
    london.compress[variable] <- london.compress[variable] - mean(london.compress[[variable]])
}

# head(london.compress)

```

## Overall

### Feature selection for 'overall' model

```{r}
o.all.mod <- as.formula("overall ~ LZeq + LCeq + LAeq + LAmax + LA_10 + LA_50 + LA_90 + N + Nmax + N10 + N50 + N90 + R + R5 + R10 + R50 + R90 + R95 + S + Smax + S10 + S50 + S90 + T + Tmax + T10 + T50 + T90 + FS + FSmax + FS10 + FS50 + FS90 + FS95 + THD + THDmax + THD10 + THD50 + THD90 + I + Imax + I5 + I10 + I50 + I90 + I95 + SIL.rms. + SIL10 + SIL50 + SIL90 + LA5_LA95 + SpectralCentroid + PeakSpectralCentroid + HighFreqAvg + PeakHighFreqAvg + FS_slope + THD_slope + I_slope + LA_slope + LZ_slope + N_slope + R_slope + S_slope + T_slope + (1|LocationID)")


o.full.mod <- lmerTest::lmer(o.all.mod, data = london.compress)
o.step.mod <- lmerTest::step(o.full.mod, direction = 'both', reduce.random=F)
print(o.step.mod)

```

The selected model is:

```{r}
o.selected.mod <- get_model(o.step.mod)
summary(o.selected.mod)
r.squaredGLMM(o.selected.mod)

```

overall ~ LAeq + Nmax + R90 + Smax + FS90 + FS95 + I + I5 + SIL.rms. + FS_slope + N_slope + R_slope + S_slope + (1|LocationID)

From here we can investigate more thorougly, starting with multicollinearity and VIF

### Multicollinearity

```{r}
vif(o.selected.mod, data = london.compress)
```

LAeq, FS90, FS95, SIL.rms. all have VIF above 10

Begin by removing:
 * FS90
 * SIL.rms.

```{r}
o.mod <- lmer(overall ~ LAeq + Nmax + R90 + Smax + FS95 + I + I5 + FS_slope + N_slope + R_slope + S_slope + (1|LocationID), data = london.compress)
r.squaredGLMM(o.mod)
vif(o.mod, data = london.compress)
```

No features have VIF > 10. The highest VIF features are the _slope features.


### Predicting Overall responses and Checking prediction behaviour

```{r}
library(ggplot2)
london.compress$overall.pred <- predict(o.mod, newdata = london.compress)
ggplot(london.compress, aes(x=overall, y=overall.pred)) + geom_point() +
    geom_smooth(method=lm)
cor(london.compress$overall, london.compress$overall.pred)
var(london.compress$overall, london.compress$overall.pred)
print(summary(london.compress$overall))
print(summary(london.compress$overall.pred))
ggplot(london.compress, aes(x = overall, color=LocationID)) + 
    geom_density()

ggplot(london.compress, aes(x = overall.pred, color=LocationID)) + 
    geom_density()
```

## Pleasant (complex)

### Feature selection for Pleasant model

```{r}
p.all.mod <- as.formula("Pleasant ~ LZeq + LCeq + LAeq + LAmax + LA_10 + LA_50 + LA_90 + N + Nmax + N10 + N50 + N90 + R + R5 + R10 + R50 + R90 + R95 + S + Smax + S10 + S50 + S90 + T + Tmax + T10 + T50 + T90 + FS + FSmax + FS10 + FS50 + FS90 + FS95 + THD + THDmax + THD10 + THD50 + THD90 + I + Imax + I5 + I10 + I50 + I90 + I95 + SIL.rms. + SIL10 + SIL50 + SIL90 + LA5_LA95 + SpectralCentroid + PeakSpectralCentroid + HighFreqAvg + PeakHighFreqAvg + FS_slope + THD_slope + I_slope + LA_slope + LZ_slope + N_slope + R_slope + S_slope + T_slope + (1|LocationID)")

p.full.mod <- lmerTest::lmer(p.all.mod, data = london.compress)
p.step.mod <- lmerTest::step(p.full.mod, direction = "both", reduce.random = F)
print(p.step.mod)

```

The Selected model is:

```{r}
p.selected.mod <- get_model(p.step.mod)
summary(p.selected.mod)
r.squaredGLMM(p.selected.mod)
```

Pleasant ~ LA_50 + R90 + FS10 + FS90 + FS95 + THDmax + I50 + SIL50

### Multicollinearity

```{r}
vif(p.selected.mod, data = london.compress)
```

LA_50, FS90, FS95, SIL50 all have VIF > 10

Remove: 
 * FS90
 * SIL50


```{r}
p.new.mod <- lmer(Pleasant ~ LA_50 + R90 + FS10 + FS95 + THDmax + I50 + (1|LocationID), data = london.compress)
r.squaredGLMM(p.new.mod)
vif(p.new.mod, data = london.compress)
```
 
No features have VIF > 10.

### Predicting Pleasant responses and checking prediction behaviour

```{r}
london.compress$Pleasant.pred <- predict(p.new.mod, newdata = london.compress)
ggplot(london.compress, aes(x=Pleasant, y=Pleasant.pred)) + geom_point() + 
    geom_smooth(method=lm)
cor(london.compress$Pleasant, london.compress$Pleasant.pred)
var(london.compress$Pleasant, london.compress$Pleasant.pred)

print(summary(london.compress$Pleasant))
print(summary(london.compress$Pleasant.pred))

ggplot(london.compress, aes(x = Pleasant, color=LocationID)) + 
    geom_density()
ggplot(london.compress, aes(x = Pleasant.pred, color = LocationID)) + 
    geom_density()
```

## Eventful (complex)

### Feature selection for Eventful model

```{r}
e.all.mod <- as.formula("Eventful ~ LZeq + LCeq + LAeq + LAmax + LA_10 + LA_50 + LA_90 + N + Nmax + N10 + N50 + N90 + R + R5 + R10 + R50 + R90 + R95 + S + Smax + S10 + S50 + S90 + T + Tmax + T10 + T50 + T90 + FS + FSmax + FS10 + FS50 + FS90 + FS95 + THD + THDmax + THD10 + THD50 + THD90 + I + Imax + I5 + I10 + I50 + I90 + I95 + SIL.rms. + SIL10 + SIL50 + SIL90 + LA5_LA95 + SpectralCentroid + PeakSpectralCentroid + HighFreqAvg + PeakHighFreqAvg + FS_slope + THD_slope + I_slope + LA_slope + LZ_slope + N_slope + R_slope + S_slope + T_slope + (1|LocationID)")

e.full.mod <- lmerTest::lmer(e.all.mod, data = london.compress)
e.step.mod <- lmerTest::step(e.full.mod, direction = "both", reduce.random = F)
print(e.step.mod)

```

The Selected model is:

```{r}
e.selected.mod <- get_model(e.step.mod)
summary(e.selected.mod)
r.squaredGLMM(e.selected.mod)
```

Eventful ~ LA_90 + S + Smax + S50 + FS10 + THD + SIL10 + SIL90 + FS_slope + I_slope + R_slope + (1|LocationID)

### Multicollinearity

```{r}
vif(e.selected.mod, data = london.compress)
```

LA_90, S, S50, SIL90 all have VIF > 10

Remove: 
 * SIL90
 * S
 * R_slope


```{r}
e.mod <- lmer(Eventful ~ LA_90 + Smax + S50 + FS10 + THD + SIL10 + FS_slope + I_slope + (1|LocationID), data = london.compress)
r.squaredGLMM(e.mod)
vif(e.mod, data = london.compress)
```
 
No features have VIF > 10.

### Predicting Eventful responses and checking prediction behaviour

```{r}
london.compress$Eventful.pred <- predict(e.mod, newdata = london.compress)
ggplot(london.compress, aes(x=Eventful, y=Eventful.pred)) + geom_point() + 
    geom_smooth(method=lm)
cor(london.compress$Eventful, london.compress$Eventful.pred)
var(london.compress$Eventful, london.compress$Eventful.pred)

print(summary(london.compress$Eventful))
print(summary(london.compress$Eventful.pred))

ggplot(london.compress, aes(x = Eventful, color=LocationID)) + 
    geom_density()
ggplot(london.compress, aes(x = Eventful.pred, color = LocationID)) + 
    geom_density()
```

## Circumplex scatter plot

```{r}
theme_set(
    theme_bw() +
        theme(legend.position = "top")
)

# initiate a ggplot
b <- ggplot(london.compress, aes(x = Pleasant, y = Eventful, color=LocationID))

b + geom_point() + geom_rug()

# Predicted scatterplot
p <- ggplot(london.compress, aes(x = Pleasant.pred, y = Eventful.pred, color=LocationID))
p + geom_point() + geom_rug()
```



















