---
title: "R LMER Lockdown Results"
author: "Andrew Mitchell"
date: "26/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Presenting results of the Lockdown Linear mixed Effects model

Although the feature selection was completed in Python, the actual construction and application of the model have been done in R. In this notebook, I am using some useful functions in R to nicely summarise and display the final results and various tests. 

```{r, warning=FALSE, message=FALSE}
library(here)
library(readxl)
library(dplyr)

prelockdownData <- read.csv(here("data", "2020-09-01", "preLockdownData.csv"))
lockdownData <- read.csv(here("data", "2020-09-01", "lockdownData.csv"))

prelockdownDataTrain <- read.csv(here("data", "2020-09-01", "prelockdownDataTrain.csv"))
prelockdownDataTest <- read.csv(here("data", "2020-09-01", "prelockdownDataTest.csv"))

prelockdownData <- prelockdownData %>% mutate_at(vars(GroupID, LocationID), funs(as.factor))
lockdownData <- lockdownData %>% mutate_at(vars(GroupID, LocationID), funs(as.factor))

prelockdownDataTrain <- prelockdownDataTrain %>% mutate_at(vars(GroupID, LocationID), funs(as.factor))
prelockdownDataTest <- prelockdownDataTest %>% mutate_at(vars(GroupID, LocationID), funs(as.factor))

```

## Pleasant Model

```{r, warning=FALSE}
Pleasant_formula <- as.formula("Pleasant ~ LZeq + THD_95 + PeakSpectralCentroid + LZeq_10_LZeq_90 + I + (LZeq + THD_95 + PeakSpectralCentroid + LZeq_10_LZeq_90 + I|LocationID)")
init_Pleasant_model <- lmerTest::lmer(Pleasant_formula, data = prelockdownData)

step_Pleasant_model <- lmerTest::step(init_Pleasant_model, data = prelockdownData)
step_Pleasant_model
```

```{r}
Pleasant_model <- lmerTest::get_model(step_Pleasant_model)
# Pleasant_model <- lmerTest::step(Pleasant_formula, data = prelockdownData, REML=FALSE)

sjPlot::tab_model(Pleasant_model, show.icc = TRUE, collapse.ci = TRUE, show.aic = TRUE)
sjPlot::plot_model(Pleasant_model, type="re", title = "Random effects - Pleasant", show.values = TRUE)
sjPlot::plot_model(Pleasant_model, show.values = TRUE)
MuMIn::r.squaredGLMM(Pleasant_model)
```


## Eventful Model

```{r, warning=FALSE}
Eventful_formula <- as.formula("Eventful ~ R_50 + LAeq_Min + (R_50 + LAeq_Min|LocationID)")
init_Eventful_model <- lmerTest::lmer(Eventful_formula, data = prelockdownData)

step_Eventful_model <- lmerTest::step(init_Eventful_model, data = prelockdownData)
step_Eventful_model
```

```{r}
Eventful_model <- lmerTest::get_model(step_Eventful_model)


sjPlot::tab_model(Eventful_model, show.icc = TRUE, collapse.ci = TRUE, show.aic = TRUE)
sjPlot::plot_model(Eventful_model, type="re", title = "Random effects - Eventful", show.values = TRUE)
sjPlot::plot_model(Eventful_model, show.values = TRUE)
MuMIn::r.squaredGLMM(Eventful_model)

```

## Pleasant Model

```{r}
Pleasant_formula <- as.formula("Pleasant ~ LZeq + THD_95 + PeakSpectralCentroid + LZeq_10_LZeq_90 + I + (LZeq + THD_95 + PeakSpectralCentroid + LZeq_10_LZeq_90 + I|LocationID)")

Pleasant_model <- lmerTest::lmer(Pleasant_formula, data = prelockdownData, REML=FALSE)

sjPlot::tab_model(Pleasant_model, show.icc = TRUE, collapse.ci = TRUE, show.aic = TRUE)
sjPlot::plot_model(Pleasant_model, type="re", title = "Random effects - Pleasant", show.values = TRUE)
sjPlot::plot_model(Pleasant_model, show.values = TRUE)

```